Graph Generators: State of the Art and Open Challenges

### 2020-01-20 main.tex
Rev. 3 - comment fixed
Changed Arnau's affiliation

% Title portion
%\title{Graph Data Generators in the World of Big Data}
%\title{Modern Graph Generators: A Survey}
\title{Graph Generators: State of the Art and Open Challenges}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities  of which they are connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce-based implementation that is able to generate large graphs (consisting of
billions of nodes) in a reasonable time budget.

>>>>

% Title portion
%\title{Graph Data Generators in the World of Big Data}
%\title{Modern Graph Generators: A Survey}
\title{Graph Generators: State of the Art and Open Challenges}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{Sparsity-Technologies, Barcelona, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities  of which they are connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. 
The authors report that BTER is able to generate graphs with billions of edges. 
%The authors describe a highly scalable
%MapReduce-based implementation that is able to generate large graphs (consisting of
%billions of nodes) in a reasonable time budget.
